Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-25 analysis/paper/paper.Rmd
Remove notes being imported for figures only, now at start of doc

```{r software-used, echo=FALSE, message=FALSE, warning=FALSE}
rrpp <- import_notes()

rrpp_software <-
  rrpp %>% 
  transform(software_used = strsplit(software_used, ",")) %>%
  unnest(software_used) %>%
  mutate(software_used = trimws(software_used)) %>%
  mutate(software_used = toupper(software_used)) # convert all to uppercase to standardise

>>>>

```{r software-used, echo=FALSE, message=FALSE, warning=FALSE}
rrpp_software <-
  rrpp %>% 
  transform(software_used = strsplit(software_used, ",")) %>%
  unnest(software_used) %>%
  mutate(software_used = trimws(software_used)) %>%
  mutate(software_used = toupper(software_used)) # convert all to uppercase to standardise
